Synthesizing Symmetric Lenses

### 2018-06-29 papers/SymmetricLenses/main.tex
add numbers and additional info

One of reasons these algorithms are so effective, even relative to successful synthesis projects
in other domains, is because unless the same kind of data appears in a format many times,
there simply are not very many different bijections between related data formats.  Hence,
if the synthesis algorithm can find any bijection at all, then it is very likely
to be the one the user wants.  However, there is also a price for narrowing the synthesis
domain so dramatically:  Many real data formats are almost, but not quite, bijections.
More often two related data formats have some data in common, but also contain some differences.
For instance, two related tables might share four of five columns, but not the last.  Alternately, one ad hoc
configuration
file might host some format-specific meta data, such as a date, a time or reference number, whereas the other
does not.  Indeed, in our study of Augeas~\cite{augeus}, a RedHat system that
uses lenses to edit Linux files, we found that XXXXX of YYYYY lenses were not bijective.
\dpw{fill in with accurate stats and/or more concrete (and real) compelling examples; I made up the above.
mention that the POPL paper benchmarks all had to be edited?}
Consequently, past tools that search for strict bijections will rarely be applicable in practice.

@@

We implemented this\bcp{which?} algorithm and evaluated its effectiveness on a range of benchmarks
from XXXX to YYYYY. We found that ... \dpw{give a number or two that characterize
our empirical findings.}

In summary, our main contributions are:\bcp{annotate with section numbers}
\begin{itemize}
\item We define the space of simple symmetric lenses, which lies between asymmetric lenses and full symmetric lenses and has the useful property that they don't have any internal state.  We characterize
the simple lenses semantically as the subset of full symmetric lenses for which a ``forgetfulness''
property holds. We also analyze the gap between simple and full symmetric lenses empirically and argue that
simple ones suffice for many applications.
\item We show how to synthesize simple symmetric lenses (including all asymmetric lenses as a special case),
using a novel application of stochastic regular expressions to guide the search process.  In particular, we
show that the RE star semi-ring equivalences remain valid when their semantics are enriched by distributions.
\item We extend the Boomerang implementation with simple symmetric lenses, showing that they can easily be
combined with a rich variety of other lens extensions including quotients and matching lenses.  We evaluate
our implementation over a set of benchmarks drawn from XXXXX and demonstrate that YYYY ... numbers ....
\end{itemize}

>>>>

One of reasons these algorithms are so effective, even relative to successful
synthesis projects in other domains, is because unless the same kind of data
appears in a format many times, there simply are not very many different
bijections between related data formats. Hence, if the synthesis algorithm can
find any bijection at all, then it is very likely to be the one the user wants.
However, there is also a price for narrowing the synthesis domain so
dramatically: Many real data formats are almost, but not quite, bijections. More
often two related data formats have some data in common, but also contain some
differences. For instance, two related tables might share four of five columns,
but not the last. Alternately, one ad hoc configuration file might host some
format-specific meta data, such as a date, a time or reference number, whereas
the other does not. Indeed, all of our benchmarks taken from Flash
Fill~\cite{flashfill} and all of our benchmarks that synchronize file formats
contain data present in one format that isn't present in the other.
Consequently, past tools that search for strict bijections will rarely be
applicable in practice.

@@

We implemented this\bcp{which?} algorithm and evaluated its effectiveness on a
range of benchmarks, including data cleaning tasks taken from Flash Fill,
information extraction tasks taken from Augeas, and ad-hoc format
synchronization tasks taken from a variety of locations\footnote{The majority of
  these format synchronization tasks were found from the following index:
  \url{http://fileformats.archiveteam.org/wiki/Electronic_File_Formats}}.

In summary, our main contributions are:\bcp{annotate with section numbers}
\begin{itemize}
\item We define the space of simple symmetric lenses, which lies between asymmetric lenses and full symmetric lenses and has the useful property that they don't have any internal state.  We characterize
the simple lenses semantically as the subset of full symmetric lenses for which a ``forgetfulness''
property holds. We also analyze the gap between simple and full symmetric lenses empirically and argue that
simple ones suffice for many applications.
\item We show how to synthesize simple symmetric lenses (including all asymmetric lenses as a special case),
using a novel application of stochastic regular expressions to guide the search process.  In particular, we
show that the RE star semi-ring equivalences remain valid when their semantics are enriched by distributions.
\item We extend the Boomerang implementation with simple symmetric lenses,
  showing that they can easily be combined with a rich variety of other lens
  extensions including quotients and matching lenses. We evaluate our
  implementation over a set of benchmarks drawn from data cleaning, information
  extraction, and file synchronization tasks and demonstrate that we can
  synthesize all of them in under half a minute.
\end{itemize}
